%-------------------------
% Resume in Latex
% Author : Ignas Volcokas
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5 in}
\addtolength{\evensidemargin}{-0.5 in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\usepackage{ragged2e}
\justifying
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small#2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\n}
    {
    \vskip 1cm
    }
\newcommand{\p}
{
\vskip 0.5cm
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Ignas Volčokas} \\ \vspace{5pt}
    \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+15402064595}{+1 540 206 4595}
    $|$
    \faAt \hspace{.5pt} \href{mailto:ignasvolcokas@gmail.com}{ignasvolcokas@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/ignas-vol%C4%8Dokas-90a2701b4/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Iggy-V}{GitHub}
    $|$
    % \faGlobe \hspace{.5pt} \href{https://iggy-v.github.io/}{Portfolio}
    % $|$
    % \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Bogazici+University+North+Campus/@41.0863067,29.0441352,15z/data=!4m5!3m4!1s0x0:0x9d2497b07c8edb2f!8m2!3d41.0863067!4d29.0441352}{Istanbul, Turkey}
    
    \noindent\rule{8cm}{0.4pt}
\end{center}

\p
\n
Dear Hiring Manager,
\n
I am writing to express my interest in the {\it{Research Internship, Center for Sustainable Development, Global Economy and Development}} position at the Brookings Institute. With a passion for economics, social justice, and research. I am eager to contribute to the esteemed work of the Institute and learn as much as possible from the renowned team of experts.
\p
I am currently a junior Economics and Computer Science major studying at Washington and Lee University. Throughout my academic journey, I have developed a strong passion and theoretical frameworks for addressing and analyzing social issues. In classes and summer research experience, I have gained valuable technical skills, like working with Stata, Excel, and Python coding and applying these tools for data analysis.  I am confident that my blend of quantitative expertise and commitment to social impact aligns closely with the objectives and values of the Brookings Institute.
\p
My research endeavors span a wide spectrum of topics, from delving into econometrics to explore whether labor unions exhibit characteristics of a public good, to investigating the complex relationship between guns and crime. Additionally, I've analyzed the impact of Human Development Index (HDI) on international trade, and explored issues of inequality within the bail bond markets and working-class representation in the United States.
In my more qualitative classes, I have done presentations and analyzed the inequalities and injustices in the bail bond markets and have investigated the issues of working-class representation in the United States. 
\p
All these projects have developed my quantitative and qualitative skills that make me an ideal candidate for the research internship. I am confident that my multifaceted experience will not only enable me to make valuable contributions but also maximize my learning and growth opportunities within the role.
\p
I am particularly drawn to the Brookings Institute's commitment to conducting top-level research to improve policy making. Understanding social sciences, like economics, is extremely difficult because of the myriad of factors that come into play, however, good, and honest research can lead to real world impacts and improving people’s lives. I am excited about the opportunity to be part of such research. 
\p
Thank you for considering my application!  I am eager to hear back about this opportunity.
\n
Warm regards,\\
Ignas Volčokas

\end{document}
