%-------------------------
% Resume in Latex
% Author : Ignas Volcokas
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Ignas Volčokas} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+15402064595}{+1 540 206 4595}
    $|$
    \faAt \hspace{.5pt} \href{mailto:ignasvolcokas@gmail.com}{ignasvolcokas@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/ignas-vol%C4%8Dokas-90a2701b4/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Iggy-V}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://iggy-v.github.io/}{Portfolio}
    $|$
    % \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Bogazici+University+North+Campus/@41.0863067,29.0441352,15z/data=!4m5!3m4!1s0x0:0x9d2497b07c8edb2f!8m2!3d41.0863067!4d29.0441352}{Istanbul, Turkey}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Washington and Lee University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Lexington, VA, USA}
      {Major: B.Sc Computer Science;   \textbf{GPA: 4.00/4.00}}{Sep 2021 \textbf{--} May 2025}
      {2$^nd$ Major: B.A Degree in Economics; \textbf{GPA: 4.00/4.00}}{}

      {\textit{Cummilative} \textbf{GPA: 3.97/4.00}}{}
        \resumeSubHeadingListStart
        \small{\item{
            \textbf{Relevant coursework:} Software Development, Computer Organization, Programming Language Design, Algorithm Design and Analysis, Descrete Mathematics, Linear Algebra, 
            Multi-Variable Calculus, Calculus II, Mathematical Proofs, Econometrics, Statistics for Economics
             }}
            % \textbf{National University Admission Exam (YKS):} Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500. (Jul 2018)}}
        \resumeSubHeadingListEnd
    
    \resumeSubheading
      {United World College in Dilijan
      % \normalfont{(Admission rate: 0.85\%)}
      }{Dijian, Armenia}
      {International Baccalaureate;   \textbf{GPA: 41/45}}{Sep 2019 \textbf{--} May 2021}
    
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

        \textbf{Languages:}{ \emph{Python}, Java, JavaScript, TypeScript, C$++$, HTML, CSS, Haskell, Bash} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, GitHub, Unix, Flask, Node.js, SciPy, Matplotlib, AWS, Microsoft Office, Excel, Stata} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teaching Assistant}{Lexington, VA, USA}
      {Washington and Lee University, Computer Science Department}{Sep 2022 \textbf{--} Present, Part-time}
        \resumeItemListStart
            \resumeItem{Helping out in introductory programming courses. Answering student questions and guiding them in Python Labs and Office Hours. Mostly focusing on fundumental coding concepts and data structures. Hours a week: $\approx$ 6 hours.}
        \resumeItemListEnd

    \resumeSubheading
      {Summer Research Scholar}{Lexington, VA, USA}
      {Washington and Lee University}{Jun 2023 \textbf{--} Aug 2023, Full-time}
        \resumeItemListStart
            \resumeItem{10-week research experience. Project titled: Applying Genetic Algorithms to Generating Cost-Effective Test Cases for Web Applications. Supervised by Prof. Dr. Sara Sprenkle. Currently working towards a Conference Paper.}
            \resumeItem{Implemented and Compared Hill Climbing, Simulated Annealing, Genetic and Greedy algorithms for automatic test case generation in Python. Worked at high-level of abstraction; generated, and analyzed data.  Libraries used: Pandas, Matplotlib, 
            SciPy, NumPy.}
        \resumeItemListEnd
      
    \resumeSubheading
      {Editorial Associate}{Lexington, VA, USA}
      {Washington and Lee University}{Jan 2022 \textbf{--} Present, Part-time}
        \resumeItemListStart
            \resumeItem{Working for Prof. Dr. Krzysztof Jasiewic who was \textit{EEPS} journal's Head Editor.}
            \resumeItem{Proofreading new issues of the Journal. Created a database with information from all previous published articles.}
        \resumeItemListEnd

    
  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{


        \textbf{HooHacks Hackathon 2$^{nd}$ Place}{ in Education category. HooHacks is the biggest Hackathon in Virgnia. (Apr 2023)} \\ \vspace{3pt}

        \textbf{Dean's List 2021-2022, 2022-2023:}{ Awarded to top 30\% full-time students for the given academic year.} \\ \vspace{3pt}

        \textbf{Semester at Sea Davis UWC Scholarship:}{ Awarded Full Scholarship to study on Semester at Sea Fall 2023 program. Semester at Sea is a study abroad program where students study on a ship and sail around the world.} \\ \vspace{3pt}
    
        \textbf{United World College National Nomination:}{ Awarded Full Scholarship to study in United World College, 1 out of 3 people selected from Lithuania.} \\ \vspace{3pt}

      
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{EsyLearn} $|$ \emph{\href{https://github.com/Iggy-V/esyLearnHooHacks}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{EsyLearn is a project completed in HooHacks 2023 Hackathon by me and a peer. We used JavaScript, Python and CSS to create a website that served as a personal learning assistant. Once a question is asked outloud the website sends a request to ChatGPT model. Then the recieved answer is read outloud and also displayed in text. APIs used: Flask, SpeechRecognition, Recorderjs, OpenAI.}
          \resumeItemListEnd
      %
      \newblock
      %
      \resumeProjectHeading
        {\textbf{Rocket Mouse} $|$ \emph{\href{https://github.com/Iggy-V/rocketMouseIV}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A infinite runner video game written in TypeScript that utilizes Node.js. I followed a tutorial to complete this project and went further by implementing my own feature - power ups. Utilized software development principles: single responsibility, modularity, and abstraction.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Automated Daily Email} $|$ \emph{\href{https://github.com/Iggy-V/AutomatedEmail}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A python project that sends a daily email to me with a reminder to fill out a daily tracker form, sends news of the day, a picture of a dog and upcoming weather in selected locations. Introduced myself to cloud computing and deployed the project to AWS as a Lambda function.}
          \resumeItemListEnd
      
      \resumeProjectHeading
      {\textbf{YouTube Video Downloader} $|$ \emph{\href{https://github.com/Iggy-V/YouTubeDownloader}{\color{blue}GitHub}}}{}
        \resumeItemListStart
          \resumeItem{A python a project that downloads all opened YouTube video links by leveraging PyAutoGUI and PyTube libraries. Great tool to prepare for travels where internet connection is scarce.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

\section{Extracurricular Activity}
  \vspace{2pt}
    \resumeSubHeadingListStart

    \resumeSubheading
    {General Technology Society at Washington and Lee}{}
    {Event Coordinator, Executive team}{2022 \textbf{--} Present}
      \resumeItemListStart
          \resumeItem{Bringing the community together through technology. Organzing and overseeing coding projects by students.}
          \resumeItem{Organizing practice coding sessions for the student body, teaching people how to approach logical and technical questions. Topics addressed: Algorithms, Object-Oriented Programming, Design Practices. Organized around 8 sessions last term.}
      \resumeItemListEnd
    
    \resumeSubheading
    {Amnesty International at Washington and Lee}{}
    {Member, Executive team (2021-2022)}{2021 \textbf{--} Present}
    
      \resumeItemListStart
          \resumeItem{Memeber of the Amnesty International Chapter. Took minutes, scheduled meetings, improved communications between members by sending out individual to-do lists.}
          \resumeItem{As a member organized informational and fundraising events. Collected around \$5000 in donations for different relief organizations.}
      \resumeItemListEnd
    
    \resumeSubheading
    {Volleyball Club}{}
    {Member}{2019 \textbf{--} Present}
    
      \resumeItemListStart
          \resumeItem{Part of the university volleyball club team.}
          \resumeItem{I was the captain and leading practices in my high school volleyball club my senior year.}
      \resumeItemListEnd
    
    \resumeSubHeadingListEnd


%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ } \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ }
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Name}{Date}{About}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Calesenics, Ping-Pong, Board Games, Film and Photography}}
  % \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
